Background Subtraction based on Deep Feature Transformation Learning Background Subtraction

### 2018-02-02 draft.tex
test
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Your branch is up-to-date with 'origin/master'.
 Changes to be committed:
	modified:   draft.tex
revised the abstract

\begin{abstract}
% the background of problem
One of the main challenges of Background Subtraction comes from the diversity and complexity of real-world scenes.
While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks, which is named as the Deep Pixels’ Variation Learning model (DPVL).
Our main job is to find a new representation of pixels’ historical observations in a new feature space.
In this paper, videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
We conduct our training and prediction processes on block level.
The architecture of the FCN is devised from the semantic segmentation problem.
Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation.
We compare our method with some of the state-of-art methods… 
\end{abstract}

>>>>

\begin{abstract}
% 背景建模是一个复杂的问题
Background subtraction is a fundamental problem of computer vision.
% 为什么复杂
The main challenges of background subtraction comes from the diversity and the complexity of natural scenes.
% 以前的工作是怎么做的
Plenty of previous works are proposed to handle this problem by artificial model.
% 我们是怎么做的
%Previous works in this field were proposed by designing an artificial model, 
In this paper,
we propose a self-adaption solution with the utilization of convolutional neural networks, 
and a novel background subtraction model named Deep Feature Transformation Learning is proposed.
% 动机是什么
With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
% 怎么做的
The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
We conduct our training and prediction processes on block level.
The architecture of the FCN is devised from the semantic segmentation problem.
% 效果好
Comparisons with several state-of-the-art algorithms in well-known benchmark show the superiority of proposed approach.
\end{abstract}
